\chapter{Future Work}
\label{ch:Future Work}
To conclude, we will present some further aspects of this topic which either could not be elaborated within the time frame of the study or which would exceed the scope of this work. These can be carried out in further work.

\subparagraph{Using Trusted Platform Modules as Trust System for the $SPS$}
In section \ref{sec:Trust Systems} two methods for implementing a trust system were presented. On the one hand, there is a trust system based on a reputation score, as implemented in this work. On the other hand, trusted platform modules can be used to check whether users have tampered with their contributions. In further work, TPMs could be used to ensure that a report is valid. This could save the use and payment of inspectors.
\subparagraph{Extending the functionality of the prototype}
The prototype should be extended in the future. On the one hand, not all the security features presented in this paper have been implemented.  The rating, verification and reputation module still have to be implemented for the prototype. On the other hand, there are various opportunities to set up comfort functions in many places.
\subparagraph{Testing the usability of the app}
One objective of the app should be good usability, which means the implementation of the basic features and use cases should be intuitive to use. First time users should be able to book or rent out a parking space in a few clicks. We believe that we have reached this goal, but to prove it a user study would have to be prepared and conducted. This could done as a part of a follow-up work.
\subparagraph{Testing the performance of the app}
The same applies to performance. Our app should show consistently good performance, preventing annoying waiting or loading times for the user. The verification of the performance could also be carried out in a user study.
\subparagraph{Proving the profitability of the $SPS$}
If a service provider wanted to realize the $SPS$, it should be verified beforehand that the system will in total generate profits and not losses. Although the $SPS$ was developed with this property in mind, test models and calculations would have to be carried out to check its profitability. Such models and calculations are outside the scope of an computer science bachelor thesis like this one, but can be carried out in future work.
